Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-12 manuscript.tex
section 6 revision

The different RV estimates all appear to follow a similar exponential decay. \xavier{If we analyse each RV estimate individually, we see that all the measurements, even though from three different stars, follow the same curve. This implies that for the stars considered, the precision in each RV estimate is driven by the SNR of the analysed spectra.} This is not surprising as the three stars studied have very similar spectral types. They are all main sequence K-dwarfs.

>>>>

The different RV estimates all appear to follow a similar exponential decay. \xavier{Considering each RV estimate individually, it appears that all the measurements follow the same curve even though the measurements are from three different stars. This suggests that for the stars considered, the precision in each RV estimate may be driven by the SNR of the analyzed spectra.} This is not surprising as the three stars studied have very similar spectral types. They are all main sequence K-dwarfs.
